Experiment 1

### 2021-07-09 experiments/experiment 1/experiment 1.Rmd
New microxanox version 0.2.1 - no functinal changes

microxanox_release <- "0.2"

@@

# remotes::install_github(
#   "UZH-PEG/microxanox",
#   ref = "0.2",
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE
# )

>>>>

microxanox_release <- "0.2.1"

@@

# remotes::install_github(
#   "UZH-PEG/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE
# )
